\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Huang, Han-Xuan} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{Tel: +886 903712400 \quad E-mail: sigtunatw@gmail.com \quad Website: \href{https://ntut-xuan.github.io}{https://ntut-xuan.github.io}}  %

\begin{document}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
{\bf BS in Computer Science and Information Engineering} \hfill {2020/09 - 2024/06} \\
{National Taipei University of Technology, Taipei, Taiwan.}
\begin{itemize}
  \item GPA: 3.77/4.0
  \item {
    Outstanding in Computer Programming (Score: 100), 
    Networking Programming (Score: 98), 
    Object-Oriented Programming (Score: 95), 
    Web Programming (Score: 95),
    and Network Security (Score: 92).
  }
\end{itemize}
\end{rSection}

\begin{rSection}{PROJECTS}
{\bf NuOJ (Nu Online Judge) \hfill {Student Graduation Project (Project Lead, Backend Developer)}}
    \begin{itemize}
        \item {Duration: 2021/02 - now (Developing)}
        \item {Technologies used: {\bf Flask, Docker, Unit Tests, CI (GitHub Action), Swagger}, Sandbox (Isolate).}
        \item {Provide a platform to host the programming contest or programming education. The platform implemented sandboxes with strict permission to prevent attacks like covert channels, large file generation, and memory space exhaustion. The project also has characteristics like quickly deploying with Docker containerization and enhancing software quality through unit testing and static type checking.}
    \end{itemize}

{\bf School Epidemic Report System \hfill {Final Project (Project Lead, Android and Full-Stack Developer)}}
    \begin{itemize}
        \item {Duration: 2022/02 - 2022/06 (Public Archived)}
        \item {Technologies used: {\bf Flask}, Android (Java), TailwindCSS, JavaScript}
        \item {Equip with the Android app client and the Web CMS. The application can notify all students enrolled in the same course as the confirmed cases and have a page to demonstrate daily and total confirmed cases.}
    \end{itemize}
\end{rSection}

\begin{rSection}{EXPERIENCE}
{\bf Computer Skills Foundation, Taipei, Taiwan \hfill {Project Lead Developer, Contract}} \\
2023/02 - 2023/06
    \begin{itemize}
        \item {Technologies used: Java, JUnit, ReadTheDocs}
        \item {Develop the project in the second phase, which supports Go and C\verb|#| language on analysis software that calculates programming similarity in other samples in percentage. We also enhance the software quality through unit testing and creating documentation for the software to improve the user experience.}
    \end{itemize}

{\bf National Taipei University of Technology, Taipei, Taiwan \hfill {Teacher Assistance, Contract}} \\
{2022/09 - 2023/06}
    \begin{itemize}
        \item {Technologies used: C++, OOP, Jenkins, Cyber Security, MVC, Unit Tests, Gcovr}
        \item {TA of the Object-Oriented Programming and Object-Oriented Programming Labs course. The duty of Ta is assist the students in understanding and applying programming concepts, develop and maintain an Online Judge system based on Jenkins platform, and implement security measures to prevent cheating and protect the system from potential attacks.}
    \end{itemize}
    
{\bf Computer Skills Foundation, Taipei, Taiwan \hfill {Project Lead Developer, Contract}} \\
2022/02 - 2022/09
    \begin{itemize}
        \item {Technologies used: Java}
        \item {Develop the project in the first phase, which design and implement a plagiarism analysis software equip three distinct methods to calculate programming similarity in other samples in percentage.}
    \end{itemize}
\end{rSection} 

\newpage

\begin{rSection}{SELF-PROMOTION}
    I'm Huang, Han-Xuan. As a Flask backend developer, I have a strong foundation in Python and a keen interest in learning new technologies to enhance my development skills. I have experience with how to design web applications and how to improve software quality with unit tests and CI checks. I am eager to contribute to the team while also advancing my growth. 

    About my personality, I enjoy sharing the relevant technology that I have learned with others. Each time I develop a project, I always have certain expectations for it and will try to research and achieve the expectations of the project. I often take on the role of team leader and adjust the tasks according to the abilities of team members while also trying to cultivate their learning of new skills.

    In my experience as a Python backend developer, I have experience using Python SQL toolkits like SQLAlchemy to develop the application with the database. Moreover, I frequently use some tools to make the project robust. For example, I use pre-commit to run Black and ensure that my code conforms to the style guidelines outlined in PEP8 before being pushed to GitHub. Additionally, I use Pytest to write the unit tests, ensuring that the software runs smoothly and that the project remains stable with a test coverage rate of 85 percent or higher. I also use GitHub Actions to run Continuous Integration to verify that each commit can build successfully in Docker, passes the unit tests, passes static-type checking with Mypy, and monitor test coverage using Codecov. After the measures to make the project robust, it should improve the development experience to decrease the debugging time and improve the software quality to reduce the number of times bugs occur. I have successfully implemented these measures in my projects like NuOJ or FastShop, where they have proven effective in minimizing errors during development, as noted by my collaborators.
    
    As an intern, I would like to study how to develop a web application that considers the load issue and how to optimize the loads and distribute the load to multiple machines. Furthermore, I would like to learn how to collaborate effectively with teams to increase project development efficiency and improve relationships with development partners. Finally, I am committed to improving my development skills, including Clean Code and Clean Architecture, to enhance project robustness.
    
    Thank you for considering my application. I look forward to discussing how I can contribute as an intern.
\end{rSection}
\end{document}
